Model of Models' stuff

### 2023-06-26 minos/testing/model_of_models_work.Rmd

```{r}
# note this is the path to the rate of change models, NOT the regenerative mean effects
mod.path <- 'Minos/data/transitions/hh_income/ols2/'
m1 <- readRDS(paste0(mod.path, 'hh_income_2009_2010.rds'))
m2 <- readRDS(paste0(mod.path, 'hh_income_2010_2011.rds'))
m3 <- readRDS(paste0(mod.path, 'hh_income_2011_2012.rds'))
m4 <- readRDS(paste0(mod.path, 'hh_income_2012_2013.rds'))
m5 <- readRDS(paste0(mod.path, 'hh_income_2013_2014.rds'))
m6 <- readRDS(paste0(mod.path, 'hh_income_2014_2015.rds'))
m7 <- readRDS(paste0(mod.path, 'hh_income_2015_2016.rds'))
m8 <- readRDS(paste0(mod.path, 'hh_income_2016_2017.rds'))
m9 <- readRDS(paste0(mod.path, 'hh_income_2017_2018.rds'))
m10 <- readRDS(paste0(mod.path, 'hh_income_2018_2019.rds'))
m11 <- readRDS(paste0(mod.path, 'hh_income_2019_2020.rds'))
```

@@

>>>>

```{r}
# note this is the path to the rate of change models, NOT the regenerative mean effects
mod.path <- 'Minos/data/transitions/hh_income/ols/'
m1 <- readRDS(paste0(mod.path, 'hh_income_2009_2010.rds'))
m2 <- readRDS(paste0(mod.path, 'hh_income_2010_2011.rds'))
m3 <- readRDS(paste0(mod.path, 'hh_income_2011_2012.rds'))
m4 <- readRDS(paste0(mod.path, 'hh_income_2012_2013.rds'))
m5 <- readRDS(paste0(mod.path, 'hh_income_2013_2014.rds'))
m6 <- readRDS(paste0(mod.path, 'hh_income_2014_2015.rds'))
m7 <- readRDS(paste0(mod.path, 'hh_income_2015_2016.rds'))
m8 <- readRDS(paste0(mod.path, 'hh_income_2016_2017.rds'))
m9 <- readRDS(paste0(mod.path, 'hh_income_2017_2018.rds'))
m10 <- readRDS(paste0(mod.path, 'hh_income_2018_2019.rds'))
m11 <- readRDS(paste0(mod.path, 'hh_income_2019_2020.rds'))
```

@@

# hh_income

```{r}
income <- all.years.long %>%
  filter(grepl("hh_income", Predictor))

ggplot(income, aes(x = year, y = coefficient, group=1)) +
  geom_line() +
  labs(title = 'Household Income')
```
